---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rSpectral

<!-- badges: start -->
<!-- badges: end -->

The goal of rSpectral is to make Spectral Modularity graph clustering method  available to most of R graph frameworks.

## Installation

You can install the development version of rSpectral from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cmclean5/rSpectral")
```

## Example

This is a basic example which shows you how to solve a common problem

1. load the karate club graph:
```{r example}
library(rSpectral)
library(igraph)
data(karate, package="igraphdata")
l<-layout_nicely(karate)
```

2. store graph's edges as data.frame
```{r }

el = as.data.frame(get.edgelist(karate,names=T))

rSpectral::load_data(df=el)
```

3. run spectral clustering on graph
```{r }
status = rSpectral::spectral(fix_neig=0)
spec0   = rSpectral::membership(detach_graph=0)

idx<-match(V(karate)$name,spec0$ID)
mem0<-spec0$K[idx]
```

4. plot the graph with membership colors
```{r }
palette <- rainbow(max(as.numeric(mem0)))
plot(karate,vertex.color=palette[mem0],layout=l)
```

5. run spectral clustering on graph, fixing neighbouring nodes found 
in same community
```{r }
status = rSpectral::spectral(fix_neig=1)
spec1   = rSpectral::membership(detach_graph=0)
idx<-match(V(karate)$name,spec1$ID)
mem1<-spec1$K[idx]
```

6. and plot again
```{r }
palette <- rainbow(max(as.numeric(mem1)))
plot(karate,vertex.color=palette[mem1],layout=l)
```

7. run spectral clustering - fixing neighbouring nodes, Cnmin=5
```{r }
status = rSpectral::spectral(fix_neig=1,Cn_min=5)
spec1.5   = rSpectral::membership(detach_graph=1)
idx<-match(V(karate)$name,spec1.5$ID)
mem1.5<-spec1.5$K[idx]
```

Note, in the last call to \code{membership} we use \code{detach_graph=1}
to clear graph from the memory.

8. and the last plot
```{r }
palette <- rainbow(max(as.numeric(mem1.5)))
plot(karate,vertex.color=palette[mem1.5],layout=l)
```


In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
