---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rSpectral

<!-- badges: start -->
<!-- badges: end -->

The goal of 'rSpectral' is to make Spectral Modularity graph clustering method  available to most of R graph frameworks.

## Installation

You can install the development version of rSpectral from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cmclean5/rSpectral")
```

## Example

This is a basic example which shows you how to solve a common problem

1. load the karate club graph and plot Faction membership:
```{r karate.example}
library(rSpectral)
library(igraph)
data(karate, package="igraphdata")
l<-layout_nicely(karate)
memT<-V(karate)$Faction
palette <- rainbow(max(as.numeric(memT)))
plot(karate,vertex.color=palette[memT],layout=l)
```

2. run spectral clustering on graph
```{r rspec.default}
mem0<-igraph::membership(rSpectral::spectral_igraph_communities(karate))
```

3. plot the graph with membership colors
```{r plot.rspec.default}
palette <- rainbow(max(as.numeric(mem0)))
plot(karate,vertex.color=palette[mem0],layout=l)
```

4. run spectral clustering on graph, fixing neighbouring nodes found 
in same community
```{r rspec.fixneig}
mem1<-igraph::membership(
  rSpectral::spectral_igraph_communities(karate, fix_neig=1))
```

5. and plot again
```{r plot.rspec.fixneig}
palette <- rainbow(max(as.numeric(mem1)))
plot(karate,vertex.color=palette[mem1],layout=l)
```

6. run spectral clustering - fixing neighbouring nodes, Cnmin=5
```{r rspec.fixneig.cnmin}
mem1.5<-igraph::membership(
  rSpectral::spectral_igraph_communities(karate, fix_neig=1,Cn_min=5))
```

5. and the last plot
```{r plot.rspec.fixneig.cnmin}
palette <- rainbow(max(as.numeric(mem1.5)))
plot(karate,vertex.color=palette[mem1.5],layout=l)
```


`GraphNEL` objects could be processed similarily, all other graph types could be
converted either to `igraph` or to `GraphNEL` by packages such as `Intergraph`.